Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-13 tsibbletalk.Rmd
fig caps

---
title: "Conversations in time: interactive visualisation to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address: Auckland, New Zealand
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address: Melbourne, Australia
  email: dicook@monash.edu
bibliography: tsibbletalk.bib
abstract: >
  The \pkg{tsibbletalk} package can be used to interactively explore temporal data
  of nesting and crossing structures, and discover interesting periodic/aperiodic
  slices. This package implements a shared `tsibble` object that allows for
  linked brushing for coordinated views, and a shiny module that aids in wrapping
  time lines for seasonal patterns. The basic usage of functions is demonstrated
  in the article, wit data examples.
preamble: |
  \usepackage{subfig}
output: rticles::rjournal_article
---

@@

```{r highlight-retail, fig.height = 6, out.width = ".49\\linewidth", fig.show = "hold", fig.cap = "ToDo", fig.subcap = c("1", "2"), fig.ncol = 2}
```

@@

As opposed to one-to-one linking, \CRANpkg{tsibbletalk} defaults to categorical linking where marking one or more observations in one category will broadcast to all other observations in this category. Given time series plots, click any data point on a line, highlighting the whole line as a result. The `as_shared_tsibble()` uses `tsibble`'s `key` variables to achieve these types of linking, and the `spec` argument takes one step further in constructing hybrid linking, such as hierarchical and categorical linking. For example, each series in the `aus_retail` data corresponds to all possible combinations of the `State` and `Industry` variables. They are intrinsically crossed with each other. If one variable is nested within another, this lends itself to a hierarchical structure, like geographical hierarchy. Such collection of inter-related time series are referred to as hierarchical and grouped time series in the literature [@fpp].

@@

```{r tourism-linking-fig, fig.cap = "ToDo"}
include_graphics("img/tourism-linking.png")
```

This dataset contains a three-level hierarchy: the root node is implicitly Australia, and geographically disaggregated to states and lower-level tourism regions. A new handy function `plotly_key_tree()` has been implemented to address the need of hierarchical discovery arising from the data. It interprets hierarchies in the shared tsibble's `spec` as a tree view, built with \CRANpkg{plotly}. The following code line produces the linked tree diagram and fills the left panel of Figure \ref{fig:tourism-linking-fig}. The visual of tree hierarchy untangles a group of related series and snapshots the data organisation from a bird's eye view.

@@

```{r wrap-ped, fig.show = "hold", fig.cap = "ToDo", fig.subcap = c("(1)", "(2)", "(3)"), fig.ncol = 1}
include_graphics("img/wrap-0.png")
include_graphics("img/wrap-1.png")
include_graphics("img/wrap-7.png")
```

>>>>

---
title: "Conversations in time: interactive visualisation to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address: Auckland, New Zealand
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address: Melbourne, Australia
  email: dicook@monash.edu
bibliography: tsibbletalk.bib
abstract: >
  The \pkg{tsibbletalk} package can be used to interactively explore temporal data
  of nesting and crossing structures, and discover interesting periodic/aperiodic
  slices. This package implements a shared `tsibble` object that allows for
  linked brushing for coordinated views, and a shiny module that aids in wrapping
  time lines for seasonal patterns. The basic usage of functions is demonstrated
  in the article, with data examples.
preamble: |
  \usepackage{subfig}
output: rticles::rjournal_article
---

@@

```{r highlight-retail, fig.height = 6, out.width = ".49\\linewidth", fig.show = "hold", fig.cap = "Plots for the \\code{aus\\_retail} data, with the series of strongest seasonal strength highlighted. (a) An overlaid time series plot. (b) A scatter plot drawn from their time series features, where each dot represents a time series from (a).", fig.subcap = c("", ""), fig.ncol = 2}
```

@@

As opposed to one-to-one linking, \CRANpkg{tsibbletalk} defaults to categorical linking where marking one or more observations in one category will broadcast to all other observations in this category. Given time series plots, click any data point on a line, highlighting the whole line as a result. The `as_shared_tsibble()` uses `tsibble`'s `key` variables to achieve these types of linking, and the `spec` argument takes one step further in constructing hybrid linking, for example hierarchical and categorical linking. For example, each series in the `aus_retail` data corresponds to all possible combinations of the `State` and `Industry` variables. They are intrinsically crossed with each other. If one variable is nested within another, this lends itself to a hierarchical structure, like geographical hierarchy. Such collection of inter-related time series are referred to as hierarchical and grouped time series in the literature [@fpp].

@@

```{r tourism-linking-fig, fig.cap = "Coordinated views generated from the \\code{tourism\\_shared} with persistent linked brushing."}
include_graphics("img/tourism-linking.png")
```

This dataset contains a three-level hierarchy: the root node is implicitly Australia, and geographically disaggregated to states and lower-level tourism regions. A new handy function `plotly_key_tree()` has been implemented to address the need of hierarchical discovery arising from the data. It interprets hierarchies in the shared tsibble's `spec` as a tree view, built with \CRANpkg{plotly}. The following code line produces the linked tree diagram and spans the left panel of Figure \ref{fig:tourism-linking-fig}. The visual of tree hierarchy untangles a group of related series and snapshots the data organisation from a bird's eye view.

@@

```{r wrap-ped, fig.show = "hold", fig.cap = "The shiny module for wrapping the \\code{pedestrian20} data.", fig.subcap = c("Initial overview state", "1-day state", "7-day state"), fig.ncol = 1}
include_graphics("img/wrap-0.png")
include_graphics("img/wrap-1.png")
include_graphics("img/wrap-7.png")
```

### 2020-09-13 tsibbletalk.tex
fig caps

\abstract{%
The \pkg{tsibbletalk} package can be used to interactively explore
temporal data of nesting and crossing structures, and discover
interesting periodic/aperiodic slices. This package implements a shared
\texttt{tsibble} object that allows for linked brushing for coordinated
views, and a shiny module that aids in wrapping time lines for seasonal
patterns. The basic usage of functions is demonstrated in the article,
wit data examples.
}

@@

{\centering \subfloat[1\label{fig:highlight-retail-1}]{\includegraphics[width=.49\linewidth]{figure/highlight-retail-1} }\subfloat[2\label{fig:highlight-retail-2}]{\includegraphics[width=.49\linewidth]{figure/highlight-retail-2} }

@@

\caption[ToDo]{ToDo}\label{fig:highlight-retail}
\end{figure}
\end{Schunk}

@@

As opposed to one-to-one linking, \CRANpkg{tsibbletalk} defaults to
categorical linking where marking one or more observations in one
category will broadcast to all other observations in this category.
Given time series plots, click any data point on a line, highlighting
the whole line as a result. The \texttt{as\_shared\_tsibble()} uses
\texttt{tsibble}'s \texttt{key} variables to achieve these types of
linking, and the \texttt{spec} argument takes one step further in
constructing hybrid linking, such as hierarchical and categorical
linking. For example, each series in the \texttt{aus\_retail} data
corresponds to all possible combinations of the \texttt{State} and
\texttt{Industry} variables. They are intrinsically crossed with each
other. If one variable is nested within another, this lends itself to a
hierarchical structure, like geographical hierarchy. Such collection of
inter-related time series are referred to as hierarchical and grouped
time series in the literature \citep{fpp}.

@@

\caption[ToDo]{ToDo}\label{fig:tourism-linking-fig}
\end{figure}
\end{Schunk}

This dataset contains a three-level hierarchy: the root node is
implicitly Australia, and geographically disaggregated to states and
lower-level tourism regions. A new handy function
\texttt{plotly\_key\_tree()} has been implemented to address the need of
hierarchical discovery arising from the data. It interprets hierarchies
in the shared tsibble's \texttt{spec} as a tree view, built with
\CRANpkg{plotly}. The following code line produces the linked tree
diagram and fills the left panel of Figure
\ref{fig:tourism-linking-fig}. The visual of tree hierarchy untangles a
group of related series and snapshots the data organisation from a
bird's eye view.

@@

{\centering \subfloat[(1)\label{fig:wrap-ped-1}]{\includegraphics[width=\textwidth]{img/wrap-0} }\newline\subfloat[(2)\label{fig:wrap-ped-2}]{\includegraphics[width=\textwidth]{img/wrap-1} }\newline\subfloat[(3)\label{fig:wrap-ped-3}]{\includegraphics[width=\textwidth]{img/wrap-7} }

@@

\caption[ToDo]{ToDo}\label{fig:wrap-ped}
\end{figure}
\end{Schunk}

>>>>

\abstract{%
The \pkg{tsibbletalk} package can be used to interactively explore
temporal data of nesting and crossing structures, and discover
interesting periodic/aperiodic slices. This package implements a shared
\texttt{tsibble} object that allows for linked brushing for coordinated
views, and a shiny module that aids in wrapping time lines for seasonal
patterns. The basic usage of functions is demonstrated in the article,
with data examples.
}

@@

{\centering \subfloat[\label{fig:highlight-retail-1}]{\includegraphics[width=.49\linewidth]{figure/highlight-retail-1} }\subfloat[\label{fig:highlight-retail-2}]{\includegraphics[width=.49\linewidth]{figure/highlight-retail-2} }

@@

\caption[Plots for the \code{aus\_retail} data, with the series of strongest seasonal strength highlighted]{Plots for the \code{aus\_retail} data, with the series of strongest seasonal strength highlighted. (a) An overlaid time series plot. (b) A scatter plot drawn from their time series features, where each dot represents a time series from (a).}\label{fig:highlight-retail}
\end{figure}
\end{Schunk}

@@

As opposed to one-to-one linking, \CRANpkg{tsibbletalk} defaults to
categorical linking where marking one or more observations in one
category will broadcast to all other observations in this category.
Given time series plots, click any data point on a line, highlighting
the whole line as a result. The \texttt{as\_shared\_tsibble()} uses
\texttt{tsibble}'s \texttt{key} variables to achieve these types of
linking, and the \texttt{spec} argument takes one step further in
constructing hybrid linking, for example hierarchical and categorical
linking. For example, each series in the \texttt{aus\_retail} data
corresponds to all possible combinations of the \texttt{State} and
\texttt{Industry} variables. They are intrinsically crossed with each
other. If one variable is nested within another, this lends itself to a
hierarchical structure, like geographical hierarchy. Such collection of
inter-related time series are referred to as hierarchical and grouped
time series in the literature \citep{fpp}.

@@

\caption[Coordinated views generated from the \code{tourism\_shared} with persistent linked brushing]{Coordinated views generated from the \code{tourism\_shared} with persistent linked brushing.}\label{fig:tourism-linking-fig}
\end{figure}
\end{Schunk}

This dataset contains a three-level hierarchy: the root node is
implicitly Australia, and geographically disaggregated to states and
lower-level tourism regions. A new handy function
\texttt{plotly\_key\_tree()} has been implemented to address the need of
hierarchical discovery arising from the data. It interprets hierarchies
in the shared tsibble's \texttt{spec} as a tree view, built with
\CRANpkg{plotly}. The following code line produces the linked tree
diagram and spans the left panel of Figure
\ref{fig:tourism-linking-fig}. The visual of tree hierarchy untangles a
group of related series and snapshots the data organisation from a
bird's eye view.

@@

{\centering \subfloat[Initial overview state\label{fig:wrap-ped-1}]{\includegraphics[width=\textwidth]{img/wrap-0} }\newline\subfloat[1-day state\label{fig:wrap-ped-2}]{\includegraphics[width=\textwidth]{img/wrap-1} }\newline\subfloat[7-day state\label{fig:wrap-ped-3}]{\includegraphics[width=\textwidth]{img/wrap-7} }

@@

\caption[The shiny module for wrapping the \code{pedestrian20} data]{The shiny module for wrapping the \code{pedestrian20} data.}\label{fig:wrap-ped}
\end{figure}
\end{Schunk}
